---
title: "{{TITLE}}"
author:
  - name: "{{AUTHOR}}"
    affiliations:
      - "{{INSTITUTION}}"
date: today
format:
  html:
    toc: true
    code-fold: true
  docx:
    reference-doc: null
  pdf:
    documentclass: article
    geometry: margin=1in
bibliography: references.bib
csl: apa.csl
execute:
  echo: false
  warning: false
  message: false
---

## Abstract

{{ABSTRACT}}

**Keywords:** {{KEYWORDS}}

## Introduction

{{INTRODUCTION}}

## Theoretical Background

### {{CONSTRUCT_1}}

### {{CONSTRUCT_2}}

### Hypotheses

Based on the theoretical framework above, we propose:

**H1:**

**H2:**

**H3:**

## Method

### Participants and Procedure

### Measures

#### {{MEASURE_1}}

#### {{MEASURE_2}}

### Analytical Strategy

## Results

### Descriptive Statistics

```{r}
#| label: tbl-descriptives
#| tbl-cap: "Descriptive Statistics and Correlations"

# Load from targets pipeline:
# targets::tar_read(table1)
```

### Hypothesis Tests

#### Hypothesis 1

```{r}
#| label: tbl-h1
#| tbl-cap: "Hypothesis 1 Results"

# targets::tar_read(h1_model) |> modelsummary::modelsummary()
```

#### Hypothesis 2

### Robustness Checks

## Discussion

### Theoretical Contributions

### Practical Implications

### Limitations and Future Directions

## Conclusion

## References
